\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[left=1in,top=0.6in,right=1in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{microtype}
\pagenumbering{gobble}
\hypersetup{hidelinks}
\usepackage[none]{hyphenat}
\emergencystretch=2em
\begin{document}
\begin{center}
  {\Huge\bfseries Valerie Dryden}\\[2pt]
  {\large Fractional CTO | Executive Coach | Transformation Expert}\\[6pt]
  {\small
    \href{mailto:outragedpinkracoon@gmail.com}{outragedpinkracoon@gmail.com} |
    07984589806 |
    Glasgow, Scotland |
    \href{https://www.linkedin.com/in/outragedpinkracoon}{linkedin.com/in/outragedpinkracoon}
  }
\end{center}
\vspace{0.5em}

\section*{Professional Summary}
Fractional CTO and ILM Level 5 certified executive coach with nearly two decades in tech, specialising in engineering leadership, technology transformation across Series A–G companies in complex, regulated environments (ISO 27k and 13485). 300+ people coached including 100+ founders. I bring direct, no-nonsense executive leadership instead of generic frameworks and playing corporate theatre.

In the last 6 years alone I've led multi-million dollar transformations across 5 companies at executive level, with teams of 10–150+ engineers and budgets up to £20M, in companies up to \$300M ARR across MedTech, FinTech, LawTech, InsurTech and AppSec.

Consistent track record of cutting cycle times by 60\%, reducing incidents by 50\%, saving £1m+ annually through delivery transformation and AI adoption, and delivering cloud migrations with zero downtime.

\section*{Experience}

\subsection*{Doccla | VP of Engineering (Acting CTO) \small (Feb 2025 -- Present)}
\subsubsection*{\$32M HealthTech Series B | UK Remote | Elixir, Clojure, C\#, Multi-cloud}

As VP of Eng/Acting CTO at Doccla, I align product, engineering, AI, data, and operations under a unified technical vision. I am accountable for predictable, high-quality delivery while coaching and growing leaders across the organisation.

\begin{itemize}
  \item Reduced engineering cycle time by \textbf{60\%} through targeted investment and transformation.
  \item Scaled AI adoption to \textbf{80\%} of engineers, improving delivery speed and consistency.
  \item Championed the use of ElevenLabs voice LLM in the platform to reduce operational costs by 50\%.
  \item Led \textbf{ISO 27001/13485} audit delivery, achieving \textbf{100\% Vanta compliance} ahead of schedule; implemented a lightweight and compliant SDLC.
  \item Delivered the Azure/GCP to AWS migration with \textbf{zero downtime} under strict customer deadlines.
  \item Led end-to-end cross-functional delivery of bespoke enterprise programmes unlocking \textbf{\pounds1m+} revenue.
  \item Turned around team culture by coaching leaders and resetting norms (feedback, accountability, psychological safety), lifting \textbf{eNPS from -50 to +64}.
  \item Strengthened operational resilience through incident management and observability, reducing defects by \textbf{40\%} and incident volume by \textbf{50\%}.
\end{itemize}

\subsection*{Thirdfort | VP of Engineering (reporting to CEO) \small (Nov 2023 -- Nov 2024)}
\subsubsection*{\$20M LawTech/FinTech Series B | UK Remote | Node, React, Multi-cloud}

As VP of Engineering reporting to the CEO, I led a major technological and cultural transformation. I provided strategic and technical direction while coaching leaders and partnering with cross-functional peers to balance experience, quality, and velocity.

\begin{itemize}
  \item Led a holistic turnaround, improving delivery predictability, saving \textbf{\pounds1m+ annually}, and reducing cycle time from \textbf{24 days to 2 days}.
  \item Modernised architecture and DevOps practices, cutting release lead time by \textbf{75\%} and improving platform stability.
  \item Championed AI tooling adoption, reaching a \textbf{70\% team adoption rate} and accelerating discovery and delivery cycles.
  \item Elevated culture and career development, increasing global eNPS by \textbf{40\%}.
  \item Reduced operational costs by \textbf{25\%} through OKR discipline, vendor optimisation, and budget stewardship.
  \item Strengthened observability and risk management, reducing incidents by \textbf{20\%}.
\end{itemize}

\subsection*{Snyk | Director of Engineering (Platform) \small (Jul 2022 -- Oct 2023)}
\subsubsection*{\$7.4bn AppSec Series G | Global Remote | Node, Go, React, Multi-cloud}

As Director of Engineering for Snyk's global platform, I inherited a fragmented, fast-growing division with unclear ownership and mounting delivery pressure. Operating across authentication, authorisation, and audit in a high-throughput, 24/7 system serving a high-revenue global customer base, I brought strategic clarity, rebuilt team confidence, and created the conditions for sustainable, high-quality delivery at scale.

\begin{itemize}
  \item Cut delivery cycle time by \textbf{55\%} by clarifying domain ownership, aligning teams on measurable outcomes, and removing cross-team bottlenecks.
  \item Led the \textbf{FedRAMP} readiness programme, strengthening compliance posture and enabling expansion into the US market and unlocking multi-million dollar deals.
  \item Enabled \textbf{\$20m+ hybrid-cloud enterprise deals} by partnering with Sales and Security to develop best-in-class technical proposals and deliver pragmatic, customer-specific solutions at low COGS.
  \item Reduced incident resolution time by \textbf{34\%} by maturing on-call and support operating models and improving observability.
  \item Improved morale and ways of working, creating the first company-wide progression framework and rolling out Shape-Up across teams, achieving \textbf{eNPS of 78}.
  \item Improved hiring and onboarding at scale: increased diversity by \textbf{55\%}, raised success rate by \textbf{42\%}, and cut time-to-hire by \textbf{62\%} and time-to-10th-PR by \textbf{15 days}.
\end{itemize}

\subsection*{Zego | Head of Engineering (Platform) \small (Jul 2021 -- Jul 2022)}
\subsubsection*{\$150M InsurTech Series C | UK Remote | Scala, Python, AWS}

As Head of Engineering Platform at Zego, I stepped into a team navigating rapid scaling without the architecture or culture to support it. I defined a clear technical and cultural vision, led a major microservices rebuild, and transformed how engineering teams collaborated, delivered, and grew --- leaving the platform significantly more stable, efficient, and empowered.

\begin{itemize}
  \item Delivered a \textbf{\$30m+} microservices rebuild by aligning stakeholders to clear OKRs and sequencing delivery for measurable impact.
  \item Cut cycle time by \textbf{60\%} by redesigning team topology and eliminating cross-team delivery bottlenecks.
  \item Lowered cloud spend by \textbf{23\%} by implementing tagging, guardrails, and cost monitoring with clear ownership.
  \item Strengthened hiring posture by improving candidate satisfaction by \textbf{40\%} and increased diversity by \textbf{60\%}.
  \item Accelerated early productivity by reducing onboarding time from \textbf{14 to 3 days}.
  \item Reduced operational overhead by \textbf{30\%} by simplifying tooling and modernising platform processes.
  \item Improved delivery reliability and visibility by rolling out observability standards and DORA dashboards across engineering.
\end{itemize}

\section*{Prior Experience}

\subsection*{Care Sourcer | Director of Engineering (Reporting to CEO) \small (Feb 2019 -- Apr 2021)}
As Director of Engineering reporting to the CEO, I led technology strategy and architecture for a \pounds9m-funded startup; scaled teams and sustained delivery through COVID-era restructuring.

\subsection*{Cultivate (Deliveroo) | Senior Developer \small (Dec 2016 -- Feb 2019)}
Built and scaled 24/7, high-volume global payment and authentication systems; supported the transition from monolithic Rails to Go microservices.

\subsection*{CodeClan | Instructional Team Lead \small (Aug 2015 -- Dec 2016)}
Built and led the founding instructional team that launched Scotland's first coding academy and trained 150+ new developers in modern web development.

\subsection*{Earlier roles \small (2008 -- 2015)}
Storm ID (Senior Developer) \textbar{} Skyscanner (Web Developer) \textbar{} Electrum (Web Developer) \textbar{} Heriot-Watt (Research Assistant) \textbar{} Shepherd and Wedderburn (Junior Developer)

\section*{Advisory Roles \& Training}
Alongside senior engineering roles, I have built a complementary coaching and education practice focused on leadership development. This work directly strengthens my day-to-day impact as an engineering leader, informing how I develop teams, scale management capability, and build culture.

\begin{itemize}
    \item \textbf{Outraged Raccoon Coaching\textregistered{}} \small{(Apr 2020 -- Present)} 
    
    Partnering with Barclays Eagle Labs and TechScalar to deliver executive coaching for founders and engineering leaders across the UK, Europe, and the US. Private 1:1 coaching and training for Engineering Managers and CTOs.
    \item \textbf{Holy Sh*t I'm a Manager\texttrademark{}} \small{(Apr 2022 -- Present)} 
    
    Innovative, self-paced online Engineering Manager course; \textbf{100+} graduates and \textbf{200+} member Slack community featuring regular workshops and support groups.
\end{itemize}

\section*{Education \& Certifications}

\begin{tabular}{@{}l@{}}
\textbf{Academic}\\[0.2em]
\quad First Class Hons BSc Computer Science, Heriot-Watt (Jul 2010)\\
\quad BA Accountancy and Finance, Heriot-Watt (Jul 2006)\\[0.6em]
\textbf{Professional}\\[0.2em]
\quad Level 5 Certificate in Effective Coaching and Mentoring, ILM (Feb 2023)\\
\quad Dare to Lead\texttrademark{} trained (Jun 2021)\\
\quad Leaders Who Coach\texttrademark{} certified (Dec 2021)\\
\quad Level 3 Award in Education and Training, City \& Guilds (May 2016)
\end{tabular}

\section*{Skills}

\begin{itemize}
  \item \textbf{Engineering leadership:} executive leadership, globally distributed engineering leadership, organisational design, workforce planning, talent strategy, culture building, coaching and mentoring, training and development, stakeholder management, board-level communication, ELT collaboration.
  
  \item \textbf{Delivery \& operations:} strategic roadmapping, operating model design, operational efficiency, OKRs, KPIs, Agile delivery, DevOps, SRE, incident management, governance, risk management, change management, cost optimisation, financial stewardship, budget ownership, P\&L accountability.
  
  \item \textbf{Platform, cloud \& security:} platform modernisation, microservices and monoliths, multi-cloud and cloud infrastructure (AWS, GCP, Azure), security and compliance, audit, observability.
  
  \item \textbf{Software \& AI:} Ruby on Rails, Elixir, C\#, JavaScript, Node, Go, React, Postgres, MSSQL, AI adoption, AI automation, MCP, CI/CD, vendor management and billing.
\end{itemize}

\end{document}